Dynein project log

### 2016-07-17 thesis_stuff/thesis_stuff.tex
Fix up derivation in thesis_stuff.pdf a bit.

\begin{align*}
  \sin\left(\delta\theta\right) &\approx \delta\theta = \frac{x}{L}\\
  \delta\theta^2 &= \frac{x^2}{L^2} = \frac{Dt}{L^2}\\
\end{align*}

We set our $\tau$ to be the time when $<\delta\theta^2> \approx 1$, so:

@@

\subsection{Finding D}
For a particle feeling Brownian motion:

\begin{align*}
  \frac{\delta x}{\delta t} &= \frac{\tau}{m} R\\
\end{align*}

@@

\begin{align*}
  \frac{\delta x}{\delta t} &= \frac{\tau}{m}\sqrt{\frac{2k_BTm}{\tau \delta t}}\\
  \delta x &= \sqrt{\frac{2k_BT\tau}{m\delta t}}\\
  <\delta x^2> &= \frac{2k_BT\tau}{m}\delta t\\
\end{align*}

@@

\begin{align*}
  <\delta x^2> &= D\delta t = \frac{2k_BT\tau}{m}\delta t\\
  D = \frac{2k_BT\tau}{m}\\
\end{align*}

\subsection{Alternative derivation of D (Einstein relation)}
We can also arrive at an expression for D through an equilibrium argument. There are two forces which cause currents in solutions: drift and diffusion.
Drift is motion due to a force acting on particles. Diffusion is current due to random, natural motions of particles. Our equilibrium condition is when
the flux of particles due to both effects is equal, so there is no net particle flow. We first need to describe these fluxes:

@@

\textbf{Solving for D}
The concentration gradient in a solution is proportional to the energy gradient. By the chain rule:

@@

\textbf{Finding d$\rho$/dU}
To simplify this value, we note that, because the particles do not interact, energy is purely a function of position. Thus, by
Maxwell-Boltzman statistics, the probability of being at a location x (i.e $\rho(x)$) is proportional to $e^{-\beta U(x)}$.
From this we can find an expression for concentration and d$\rho(x)/dU(x)$:

>>>>

\begin{align*}
  \sin\left(\Delta\theta\right) &\approx \Delta\theta = \frac{x}{L}\\
  \Delta\theta^2 &= \frac{x^2}{L^2} = \frac{Dt}{L^2}\\
\end{align*}

We set our $\tau$ to be the time when $<\Delta\theta^2> \approx 1$, so:

@@

\subsection{Finding D}
For a particle feeling Brownian forces:

\begin{align*}
  \frac{\Delta x}{\Delta t} &= \frac{\tau}{m} R\\
\end{align*}

@@

\begin{align*}
  \frac{\Delta x}{\Delta t} &= \frac{\tau}{m}\sqrt{\frac{2k_BTm}{\tau \Delta t}}\\
  \Delta x &= \sqrt{\frac{2k_BT\tau}{m\Delta t}}\Delta t\\
  <\Delta x^2> &= \frac{2k_BT\tau}{m}\Delta t\\
\end{align*}

@@

\begin{align*}
  <\Delta x^2> &= D\Delta t = \frac{2k_BT\tau}{m}\Delta t\\
  D = \frac{2k_BT\tau}{m} = \frac{2k_BT}{\gamma}\\
\end{align*}

\subsection{Alternative derivation of D (Einstein relation)}
We can also arrive at an expression for D through an equilibrium argument. There are two forces which cause currents in solutions: drift and diffusion.
Drift is motion due to a force acting on particles. Diffusion is current due to random, natural motions of particles. Our equilibrium condition is when
the flux of particles due to both effects is equal, so there is no net particle flow. We first need to describe these fluxes:\\

@@

\textbf{Solving for D}\\
The concentration gradient in a solution is proportional to the energy gradient. By the chain rule:

@@

\textbf{Finding d$\rho$/dU}\\
To simplify this value, we note that, because the particles do not interact, energy is purely a function of position. Thus, by
Maxwell-Boltzman statistics, the probability of being at a location x (i.e $\rho(x)$) is proportional to $e^{-\beta U(x)}$.
From this we can find an expression for concentration and d$\rho(x)/dU(x)$:
